Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-24 manuscript.Rmd
Fixed bugs. Facets working.

evidence.summary <- full_join(evidence.summary, abstractsYear.df, 
    by = "year") %>%
    mutate(studyProp =N / N.abstracts)

@@

df <- evidence.summary

@@

>>>>

abstractsYear.df <- group_by(abstract.df, year) %>% 
    summarize(N.abstracts = n()) %>%
    mutate(year = as.numeric(year))

evidence.summary2 <- full_join(evidence.summary, abstractsYear.df, 
    by = "year") %>%
    mutate(studyProp =N / N.abstracts)

@@

df <- evidence.summary2

@@

#####################

evidence.summary3 <- select(evidence.df, -abstract) %>% 
    group_by(journal, studyType) %>%
    summarize(N = n())

evidence.summaryOverall <- select(abstract.df, -abstract) %>%
    group_by(journal) %>%
    summarize(Overall.N = n())

evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
    mutate(N.prop = N/Overall.N) %>% group_by(journal) %>%
    mutate(Overall.N.Strength = sum(N))

evidence.journalsOverall <- evidence.journals %>% group_by(journal) %>%
    mutate(Overall.N.Strength = sum(N))

journalOrder <- evidence.journalsOverall

ggplot(na.omit(evidence.journals), aes(N.prop, journal, group = journal, colour = studyType)) + geom_point(size = 3, alpha = .70) +
    theme_bw() +
    scale_colour_manual(values = cp) +
    facet_grid(.~studyType)

ggplot(na.omit(evidence.journals), aes(N, journal, group = journal, colour = studyType)) + 
    geom_segment(aes(yend = journal), xend=0, colour="grey50") +
    geom_point(alpha = .8, size = 3) + 
    scale_color_manual(values = cp) + 
    theme_bw() +
    facet_grid(.~studyType) + 
    theme(panel.grid.major.y = element_blank())
